\chapter{List of functional requirements}\label{ch:list-of-functional-requirements}
\textbf{Registration user stories}
\begin{itemize}
    \item As an unregistered user, I want to tap “Register” so that I see the registration form and register myself.
    \item As an unregistered user, I want to use my phone number to register so that my account is tied to my phone number.
    \item As an unregistered user, I want to use my e-mail address to register so that my account is tied to my e-mail address.
    \item As an unregistered user, I want to add a display name during registration so that other users can find me using it.
    \item As an unregistered user, I want to choose how to receive the registration confirmation via SMS or e-mail so that
    notification is sent to me via SMS or e-email.
    \item As an unregistered user, I want to receive the registration confirmation via SMS or Email so that I can activate my account.
    \item As a registered user, I want to confirm my email address so that I get confirmation link via email I provided.
    \item As a registered user, I want to confirm my phone number so that I use specified form to do it.
\end{itemize}

\textbf{Authentication user stories}
\begin{itemize}
    \item As a registered user, I want to authenticate myself using both combinations email-password and phone-password
    so that I use the specified form with two inputs.
    \item As a registered user, I want to restore my password if I forget it so that I use specified form and restore my password.
    \item As an authenticated user, I want my session on each device to least 7 days so that after 7 days of inactivity device
    will be logged out automatically.
\end{itemize}

\textbf{Managing contacts user stories}
\begin{itemize}
    \item As an authorized user, I want to see my contact list so that there is a list of users who are my contacts.
    \item As an authorized user, I want to search users so that I write user display name or phone number of e-mail
    address to specified input, click "Search user" button and see results.
    \item As an authorized user, I want to add other user to my contact list so that I click "Add contact" button on
    user profile and add him to my contact list.
    \item As an authorized user, I want user search input to accept empty or whitespace queries so that all users
    displayed as search result.
    \item As an authorized user, I want to remove the user from my contact list so that I click "Remove contact" button
    on user profile and remove him from my contact list.
    \item As an authorized user, I want to navigate to private chat with the user from my contact list so that I click
    "Message" button at user profile and get navigated to the private chat with him.
\end{itemize}

\textbf{Sending messages and media to individuals user stories}
\begin{itemize}
    \item As an authorized user, I want to send a text message so that another user sees my message.
    \item As an authorized user, I want to add an attachment to the message so that another user sees the message with attachment.
    \item As an authorized user, I want to add an emoji to the message so that another user sees the message with emoji.
    \item As an authorized user, I want to tap "Edit" on my message so that message I edited is changed immediately in the chat.
    \item As an authorized user, I want to tap "Delete" on my message so that message immediately disappears from the chat.
    \item As an authorized user, I want to share secret messages with users from my contact list so that our are
    messages encrypted for anyone else including system administrators.
    \item As an authorized user, I want each new message in private chats I participate to be displayed immediately
    in real-time so that I do not reload page.
\end{itemize}

\textbf{Creating and managing groups user stories}
\begin{itemize}
    \item As a registered user, I want to tap "Create channel" so that I create a new channel of the one of the types:
    Private channel, Public channel, Readonly channel.
    \item As a registered user, I want to tap "Start direct chat" so that I create a new direct chat with specified user.
    \item As a registered user, I want to tap "Start secret chat" so that I create a new secret chat with specified user.
    \item As a registered user, I want to join public groups so that I click button "Join group" to join the group.
    \item As a registered user, I want to tap "Archive" so that I archive the specified chat or channel.
    \item As a registered user, I want to tap "Un-archive" so that I un-archive the specified archived chat or channel.
    \item As a registered user, I want my secret chats to be device-specific so that I can see a secret chat only
    on the device that I used to start this chat.
\end{itemize}

\textbf{Sending messages and media to groups user stories}
\begin{itemize}
    \item As an authorized user, I want to send a text message so that other members of the group see the message I sent.
    \item As an authorized user, I want to add an attachment to the message so that other members of the group see the
    message with attachment I sent.
    \item As an authorized user, I want to add an emoji to the message so that other members of the group see the message with emoji I sent.
    \item As an authorized user, I want to tap "Edit" on my message so that other members of the group see the message I edited.
    \item As an authorized user, I want to tap "Delete" on my message so that my message is deleted for all members of the group.
    \item As an authorized user, I want to search public groups by title so that I enter display name to specified field,
    click button "Search chats" and see results.
    \item As an authorized user, I want each new message in groups I participate to be displayed immediately in
    real-time so that I do not reload page.
\end{itemize}

\textbf{Viewing messages history user stories}
\begin{itemize}
    \item As an authorized user, I want to view a message history of particular chat or group so that I see a list of
    my active chats on the UI\@.
    \item As an authorized user, I want to search messages in particular chat so that I see the results in messages
    window of the chat.
\end{itemize}

\textbf{Managing profile settings user stories}
\begin{itemize}
    \item As an authorized user, I want to update my personal information in profile settings so that other users my
    updated personal information.
    \item As an authorized user, I want to update my social network links in profile settings so that other users
    my updated social media.
    \item As an authorized user, I want to change my profile picture so that all other users will see updated one.
    \item As an authorized user, I want reset password, so that my password will change.
    \item As an authorized user, I want to tap "Logout" button so that current device will be logged out from the system.
    \item As an authorized user, I want to tap "Logout all" button so that all my authorized devices will be logged out
    from the system.
\end{itemize}