\chapter{Main aim of the work}\label{ch:main-aim-of-the-work}

The main aim of this thesis is to design and implement an instant messaging system
that copes with the required functionalities and satisfies the defined security requirements.
Implementation includes web-service (or API), web-client, desktop-client and mobile-client.
Desktop version considered to be cross-platform one.
Web service to be implemented using latest for the moment on writing this thesis .NET platform, version 5.
Web client is to be implemented using Angular front-end framework with TypeScript programming language.
Desktop client to be implemented by means of existing web client and Electron framework.
Mobile client to be implemented as an android application.
More precisely, the following steps to be done
\begin{itemize}
    \item To analyze security and user privacy vulnerabilities of instant messaging system from the prospective of three
    actors: server, communication channel, end-user.
    As a result, to propose user responsibilities among with traits of secure instant messenger application.
    \item To propose the functional and non-functional requirements for instant messaging system, based on previous
    research.
    \item To propose instant messaging system design and discuss its architectural aspects.
    \item To propose and discuss optimal authentication/authorization mechanism for our system.
    \item To discuss the security aspects of the communication channel.
    \item To design and describe user interface, which fits the functional requirements.
    \item To implement: web-service (or API), web-client, desktop-client and mobile-client.
\end{itemize}