\chapter{Introduction}\label{ch:introduction}

%----------------------------------------------------------------------------------------

\newcommand{\keyword}[1]{\textbf{#1}}
\newcommand{\tabhead}[1]{\textbf{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\bfseries#1}}
\newcommand{\option}[1]{\texttt{\itshape#1}}

%----------------------------------------------------------------------------------------


\section{General overview of Instant Messaging Systems}\label{sec:general-overview-of-im-system}
Nowadays, the Instant Messaging Systems became the most widely-used and convenient way of communication between
people via Internet.
These systems offer a simple and inexpensive way to continuance existing relationships and forming new by providing an
attractive means for sharing information and digital social interactions.
The quick development of Instant Messaging Systems and the widening of their popularity sometimes moves the focus from possible security risks.
In the worst case, Instant Messaging System exposes vulnerable to security and privacy channels to hackers and intruders
[\cite{mcclure2009hacking, mannan2005secure}].
In existing Instant Messaging Systems, there are multiple privacy and security issues that need to be resolved in order
to protect user's confidential information and shared data via these messaging applications [\cite{loesing2006privacy}].
Source [\cite{job2015modified}] gives an analysis of Telegram Messenger and the related MTProto Protocol with cryptography
behind Telegram.
Moreover, an overview of current security status for some major Instant Messaging Systems is provided.
Meanwhile, the researchers in [\cite{khan2015survey}] discussed types of threats on privacy of Instant Messaging Systems
and ranges of thereat effects for both, user and provider.
In this thesis, the most major security threats of Instant Messaging Systems is described.
In order to reflect best practices we provide a prototype-application written as example.


\section{Security vulnerabilities of Instant Messaging Systems}\label{sec:security-vulnerabilities-of-instant-messaging-systems}
\input{Chapters/security-vulnerabilities-of-instant-messaging-systems}

