\chapter{Instant messaging system requirements}\label{ch:instant-messaging-system-requirements}

In previous sections we have briefly discussed Instant Messaging System, mainly from security and user privacy aspects.
Prior to software module implementation, it is essentially important to define the functionality module will obtain.
Not to overcomplicate this section, we discuss the secure IMS requirements from customer's prospective.

There are different types of product requirements: business, functional, and non-functional.
Business requirements [INSERTREF] typically answer how the product will address the needs of your company and its users.
They also reveal the business model of the app and what problems it can solve.
Functional requirements [INSERTREF] are about functionalities that will be implemented in the app.
Non-functional requirements describe how these functionalities will be implemented.

In this article, we only focus on functional requirements [INSERTREF].
In simple words, functional requirements are not ideas of how to solve problems or which technologies to use but rather
are descriptions of software functionality.
Mostly common and simple way to define software product's functional requirements is User Stories.
User stories [INSERTREF] should be understandable both to developers and to you as the client, and should be written in simple words.
The most popular way of writing a user story is with the following formula:

\begin{center}
    "As a <user type>, I want <goal> so that <reason>."
\end{center}


\section{Modules}\label{sec:modules}


\section{Functional requirements}\label{sec:functional-requirements}
To compete with successful and commonly used instant messaging platforms, your service has to offer great functionality.
So first, let’s define the core features of a messaging app.

\begin{itemize}
    \item Registration, Authorization, Authentication
    \item Sending messages and media to individuals
    \item Manage contacts
    \item Creating groups
    \item Viewing message history
\end{itemize}
Note that Authentication [INSERTREF] means confirming your own identity, whereas Authorization [INSERTREF] means being allowed access to the
particular part of the system.

\subsection{Registration, Authorization, Authentication}\label{subsec:registration-authorization-authentication}
\begin{itemize}
    \item As an unregistered user, I want to tap “sign up” so that I can see the registration form.
    \item As an unregistered user, I want to use my phone number to register so that my account is tied to my phone number.
    \item As an unregistered user, I want to add a display name so that other users can find my account not only by my phone number.
    \item As an unregistered user, I want to receive the registration confirmation via SMS so that I can activate my account.
    \item As an unregistered user, I want to receive the registration confirmation via Email so that I can activate my account.
    \item As a registered user, I want to authorize myself using both combinations email-password and phone-password, so that I see the specified form with two inputs.
    \item As a registered user, I want to tap "logout", so that only current device will be logged out.
    \item As a registered user, I want to tap "logout all", so that all my authorized devices will be logged out.
    \item As a registered user, I want my session on each device to be 7 days, so that after 7 days of inactivity device will be logged out automatically.
    \item As a registered user, I want reset password, so that my password will change
\end{itemize}

\subsection{Manage contacts feature user stories}\label{subsec:manage-contacts-feature-user-stories}
\begin{itemize}
    \item As a registered user, I want to be able to add other users as contacts, so that each user profile has a dedicated button.
    \item As a registered user, I want to be able to blacklist other users and do not receive any messages and notification from them,
    so that each user profile has a dedicated button.
\end{itemize}

\subsection{Sending messages and media feature user stories}\label{subsec:sending-messages-and-media-feature-user-stories}
\begin{itemize}
    \item As a registered user, I want to send a text message so that another user gets a notification and sees my message.
    \item As a registered user, I want to see the status of a sent message so that I know if it’s been seen.
    \item As a registered user, I want to tap "details of message" -> "edit" on my message, so that edit the message sent by me.
    \item As a registered user, I want to tap "details of message" -> "delete" on message, so that delete the message.
\end{itemize}

\subsection{Creating groups feature user stories}\label{subsec:creating-groups-feature-user-stories}
\begin{itemize}
    \item As a registered user, I want to tap "details" -> "create group" in sidebar so that create a new group.
    \item As a registered user, I want to tap "details" -> "new chat" in sidebar, so that create a new direct chat with specified user.
    \item As a registered user, I want to join public groups, so that there is a button "join" on chat layout.
    \item As a registered user, I want to start secret chats with users from my contact list so that we can send messages that stay only on our devices.
    \item As a registered user, I want my secret chats to be device-specific so that I can see a secret chat only on the device that I used to start this chat.
    \item As a member of a secret chat, I want my secret messages to be protected from forwarding so that secret messages stay in secret chats.
    \item As a member of a secret chat, I want to get a notification when another member of the secret chat takes a screenshot of it.
\end{itemize}

\subsection{Viewing message history feature user stories}\label{subsec:viewing-message-history-feature-user-stories}
\begin{itemize}
    \item As a registered user, I want to be able to view a message history of particular chat, so that there is a list of messages of specified chat.
\end{itemize}


\section{Non-functional requirements}\label{sec:non-functional-requirements}
\begin{itemize}
    \item NFR01: The system must be enjoyable.\ We add unique ID assigned to each user and
    collect statistics about average time user spend.\ If user spends at least 2 hr.\ Average
    per day, we consider our system as enjoyable.
    \item NFR02: The system must be easy learnt.\ There is unique ID assigned to each user and
    collect the user actions statistics to the log.\ If customer ever used at least 60% of the
    total number of requirements, we consider our system to be easy learnt.
    \item NFR03: The system should be well organized.\ To fulfill this requirement, we follow an
    ISO 9241-161:2016 (en) Ergonomics of human-system interaction standard.
    \item NFR04: The system should have well performance, which meant to respond it at
    least 1 second.\ User should have a device with at least 6 GB RAM and CPU with 1.8
    GHZ, 100 Mbps internet connection.\ Server must have the following hardware: Intel
    2.4 GHz 8 Cores server processor, 64GB DDR4 (4x16GB) memory, NVME or SAS
    server disk with a minimum capacity of 1.6 TB.
    \item NFR05: The unique, unambiguous identifier of users in the system is the username. It
    is set in the application’s setting.
    \item NFR06: The UI must be well displayed with the following browsers, in the versions
    current at the date of receipt of the system (or, depending on technical possibilities,
    with the latest versions that support correct operation of the system):
    Google Chrome 72.0.36.
    Mozilla Firefox 64.0.2.
    Microsoft Edge 17.17134.
    \item NFR07: The system shall force users to use passwords with a minimum length of 8
    characters and using at least one capital letter and one number.
    \item NFR08: The UI must be compatible to use on mobile device screens with a minimum
    width of 600 pixels.
    \item NFR09: The UI must be compatible to use on desktop or laptop device screens with a
    minimum display width of 1024 pixels.
\end{itemize}