\chapter{Main aim of the work}\label{ch:main-aim-of-the-work}

The main aim of this thesis is to design and implement an instant messaging system
that copes with the required functionalities and satisfies the defined security requirements.
More precisely, the following steps
\begin{itemize}
    \item To analyze instant messaging system's security and user privacy vulnerabilities related to the three
    actors: server, communication channel, end-user.
    As a result, to propose user responsibilities among with traits of secure instant messenger application.
    \item To propose the functional and non-functional requirements for instant messaging system, based on previous
    research.
    \item To design and discuss instant messaging system, more precisely,
    \begin{itemize}
        \item To propose optimal web application architecture.
        \item To design database and propose optimal database schema.
        \item To propose planned technologies list for system's implementation.
    \end{itemize}
    \item To propose and discuss optimal authentication/authorization mechanism for instant messaging system.
    \item To discuss the security aspects of the communication channel of instant messaging system.
    \item To design and describe user interface, which fits the functional requirements of instant messaging system.
    \item The following modules are to be implemented:
    \begin{itemize}
        \item \textbf{Web Service (API).} Backend part of the project.
        Application Programming Interface that allows developers to create their own clients.
        Web service to be implemented using latest for the moment of writing of this thesis .NET 5 platform.
        \item \textbf{Web Client} –- Web version of the Mango Messenger.
        Web client to be implemented using Angular front-end framework with TypeScript programming language.
        \item \textbf{Mobile Client} –- Mobile version of the Mango Messenger for target platforms: Android, IOS\@.
        \item \textbf{Desktop Client} –- Desktop version of the Mango Messenger for target platforms Windows, Linux, MacOS\@.
        Desktop client to be implemented by means of existing web client and ElectronJS framework.
    \end{itemize}
\end{itemize}