\chapter{Project Assumptions}\label{ch:project-assumptions}


\section{Project description}\label{sec:project-description}
[Please provide an abbreviated description of the project, in line with the following structure.
The description should not be more than 10,000 characters long (including spaces).
Please use Times New Roman font, 12 pts, 1.5 spacing.]
\begin{enumerate}
    \item Research project
    \item Justification for selecting the subject
    \item Project's scope in terms of subject matter, object of research, time and space
    \item Work methodology research (method and techniques)
\end{enumerate}

Nowadays, instant messaging systems achieve a great success and became the main mean of communication
between people via an internet.
Thanks to the simplicity and quickness of the message exchanging more and more people over the world start to use
instant messengers on daily basis.
However, such a great attention forces us to discuss another aspect of these systems, an aspect of the
information security and user privacy.
The main aim of this thesis is to design and implement an instant messaging system
that copes with the required functionalities and satisfies the defined security requirements.


\section{Project objectives}\label{sec:project-objectives}
\begin{enumerate}
    \item To provide the system requirements for instant messaging system, both functional and non-functional.
    \item To analyze and propose mitigations for security and user privacy vulnerabilities of the instant messaging system.
    \item To propose web service (API's) architecture that fits the requirements.
    \item To discuss an authorization mechanism that fits the requirements.
    \item To discuss and apply E2E Encryption to the system, if necessary.
    \item To implement web service.
    \item To implement web client.
    \item To implement mobile client.
    \item To implement desktop client.
\end{enumerate}