\chapter{Security and user privacy vulnerabilities of instant messaging system}
\label{ch:security-and-user-privacy-vulnerabilities-of-instant-messaging-system}

Nowadays, the instant messaging systems became the most widely-used and convenient way of communication between
people via internet.
These systems offer a simple and inexpensive way to continuance existing relationships and forming new by providing an
attractive means for sharing information and digital social interactions.
The quick development of instant messaging systems and the widening of their popularity sometimes moves the
focus from possible security risks.
In the worst case, instant messaging system exposes vulnerable to security and privacy channels to hackers and intruders
[\cite{mcclure2009hacking, mannan2005secure}].
In existing instant messaging systems, there are multiple privacy and security issues that need to be resolved in order
to protect user's confidential information and shared data via these messaging applications [\cite{loesing2006privacy}].
The source [\cite{job2015modified}] gives an analysis of Telegram Messenger and the related MTProto Protocol with cryptography
behind the popular messenger Telegram.
Meanwhile, the researchers in [\cite{khan2015survey}] discussed types of threats on privacy of instant messaging systems
and ranges of thereat effects for both, user and provider.
There are numerous risks associated with the use of instant messaging applications and as with any form of
electronic communication one must take certain steps to mitigate those risks.
In this section we analyze security and user privacy vulnerabilities of instant messaging from the prospective of three
actors: server, communication channel, end-user.


%\section{Security and user privacy vulnerabilities of instant messaging system}
%\label{sec:security-and-user-privacy-vulnerabilities-of-instant-messaging-system}
%\input{Sections/security-and-user-privacy-vulnerabilities-of-instant-messaging-system.tex}


\section{Server vulnerabilities}\label{sec:server-vulnerabilities}


\section{Communication channel vulnerabilities}\label{sec:communication-channel-vulnerabilities}


\section{Traits of a secure instant messenger}\label{sec:traits-of-a-secure-instant-messenger}
In November 2014, the Electronic Frontier Foundation [\cite{von2010electronic}] listed seven traits that contribute to
the security of instant messengers:
\begin{itemize}
    \item Having communications encrypted in transit between all the links in the communication path.
    \item Having communications encrypted with keys the provider does not have access to (end-to-end encryption).
    \item Making it possible for users to independently verify their correspondent's identity by comparing key fingerprints.
    \item Having past communications secure if the encryption keys are stolen (forward secrecy).
    \item Having the source code open to independent review (open source).
    \item Having the software's security designs well-documented.
    \item Having a recent independent security audit.
\end{itemize}
In addition, the security of instant messengers may further be improved if they:
\begin{itemize}
    \item Do not log or store any information regarding any message or its contents.
    \item Do not log or store any information regarding any session or event.
    \item Do not rely on a central authority for the relaying of messages (decentralized computing).
\end{itemize}


\section{User responsibilities}\label{sec:user-responsibilities}
User responsibilities and procedures are as follows:
\begin{itemize}
    \item Ensure that your Instant Messaging System account password meets Carnegie Mellon
    University [\cite{shay2010encountering}] recommendations for strong passwords.
    Refer to the Guidelines for Password Management and to the Managing Your Password web pages.
    \item Download and install security upgrades from Instant Messaging System companies.
    This software is frequently updated to address security flaws.
    \item Turn on automatic updates for your Instant Messaging program and install updates as soon as they are available.
    \item Investigate encryption for your Instant Messaging client.
    The Electronic Frontier Foundation provides Instant Messaging encryption resources.
    \item Don't allow your Instant Messaging program to "remember" your password or automatically sign in to your account.
    \item Don't automatically accept incoming messages from sign-in names that are not on your contact list.
    If someone wants to begin to communicate with you via Instant Messaging System,
    they should email you or phone you to exchange Instant Messaging sign-in names.
    \item Don't accept file transfers under any circumstances.
    File transfers are an easy way for hackers to launch virus attacks and are not scanned for viruses before reaching your computer.
    In this case, sending an attachment via e-mail would be a better alternative because you
    \begin{enumerate}
        \item Expect the communication
        \item The attachment will be scanned at the mail server in addition to the anti-virus application on your computer
    \end{enumerate}
    \item Don't click links sent to you in a message, even if they appear to be from someone you know.
    Many links often go to a site hosting malware or may be malformed in such a way as to exploit another vulnerability.
    \item Protect Privacy of Sensitive Data.
    DON'T discuss via Instant Messaging System or install an Instant Messaging application on a computer containing sensitive data.
    Don't assume that your Instant Messaging conversations are private or secure.
    Most Instant Messaging programs are not encrypted.
    Therefore, someone listening on the network can read anything said in your Instant Messaging conversation.
    \item Avoid file-sharing.
    File-sharing increases the risk that unauthorized parties could gain access to the computer.
    \item Implement Virus Protection that includes network desktop and laptop solutions to handle both Instant Messaging System
    methods of delivery (Server Broker and Server Proxy).
\end{itemize}