\chapter{List of non-functional requirements}\label{ch:list-of-non-functional-requirements}
\begin{itemize}
    \item \textbf{NFR01.} Graphic user interface of the system should be well organized.
    To fulfill this requirement, we follow an ISO 9241--161:2010 (en) Ergonomics of human-system interaction
    standard [\cite{iso2010ergonomics}].
    \item \textbf{NFR02.} The system should have well performance, which meant to respond it at least 1 second.
    User should have a device with at least 6 GB RAM and CPU with 1.8 GHZ, 100 Mbps internet connection.
    Server must have the following hardware: Intel 2.4 GHz 8 Cores server processor, 64GB DDR4 (4x16GB) memory, NVME or SAS
    server disk with a minimum capacity of 1.6 TB\@.
    \item \textbf{NFR03.} The unique, unambiguous identifier of users in the system is the username.
    It is set in the profile settings.
    \item \textbf{NFR04.} The UI must be well displayed with the following browsers, in the versions
    current at the date of receipt of the system or, depending on technical possibilities,
    with the latest versions that support correct operation of the system:
    \begin{itemize}
        \item Google Chrome 72.0.36.
        \item Mozilla Firefox 64.0.2.
        \item Microsoft Edge 17.17134.
    \end{itemize}
    \item \textbf{NFR05.} The system shall force users to use passwords with a minimum length of 8
    characters and using at least one capital letter and one number and one special symbol.
    \item \textbf{NFR06.} The UI must be compatible to use on mobile device screens with a minimum
    width of 600 pixels.
    \item \textbf{NFR07.} The UI must be compatible to use on desktop or laptop device screens with a
    minimum display width of 1024 pixels.
\end{itemize}